---
title: "Interactive Graph Examples"
author: "Victoria Wallace"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here, we'll practice creating interactive graphs and tables, using built-in data sets in R packages.

- Interactive plots: {plotly}
- Interactive tables: {DT}

Note: you can use ctrl+A and the space bar to stage multiple files.
Note Part 2: Using ctrl + Shift + C, comment out selected lines of code.

```{r, include = FALSE}
# Attach packages
library(tidyverse)
library(plotly)
library(DT)
```

### A. Making an interactive graph

Using Edgar Anderson's famous 'iris' dataset

```{r, echo = FALSE, eval = FALSE}
iris_graph <- ggplot(data = iris,
                     aes(x = Petal.Width,
                         y = Petal.Length)) +
  geom_point(aes(size = Sepal.Width,
                 color = Species),
             alpha = 0.5) +
  theme_minimal() +
  labs(x = "Petal width (cm)",
       y = "Petal length (cm)",
       title = "Iris graph")

ggplotly(iris_graph)
```

# Now, an interactive table with DT.

```{r}
datatable(msleep)
```



